---
title: "Course 6 Project: Statistical Inference (Part 1)"
author: "Yun Yao"
date: "April 1, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1: Simulation Exercise

In this project I investigated the exponential distribution in R and compared it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. 

In this project, lambda was set to 0.2 for all of the simulations. I investigated the distribution of averages of 40 exponentials with a thousand simulations. 

The first step is to simulate the means of 40 exponentials a thousand times.

```{r simulation}
set.seed(123456)
lambda <- 0.2
count <- 1000
n <- 40
simulations <- matrix(rexp(count*n, rate = lambda), count, n)
means <- rowMeans(simulations)
variance <- var(means)
```
    
Now that the means of the 40 exponentials were simulated for a thousand times, let's take a look at the distribution of the sample means and variance and how they compare to the theoretical means and variance.

As shown in the plot below, the simulated means are centered around `r mean(means)`, whereas the theoretical means are centered around `r 1/lambda`. The simulated variance is `r var(means)`, and the theoretical variance is `r 1/(0.04 * 40)`.

```{r means}
# histogram of sample means
hist(means, breaks = 30, prob = TRUE, 
     main = "Distribution of Means (Exponential Distribution, lambda = 0.2)",
     ylab = "Density", xlab = "Means", cex.main = 1)
lines(density(means))
abline(v = 1/lambda, col = "red")

# histrogram of theoretical means
x <- seq(min(means), max(means), length = 100)
y <- dnorm(x, mean = 1/lambda, sd = (1/lambda/sqrt(n)))
lines(x, y, pch = 25, col = "red", lty = 2)
legend('topright', c("Simulated", "Theoretical"), 
       lty = c(1,2), col = c("black", "red"))
```

As for distribution, the Q-Q plot below shows that the simulated means follow a normal distribution, as predicted by the Central Limit Theorem.

```{r distribution}
qqnorm(means)
```
